---
title: "chat_gpt_abm"
output: html_document
author: "Natasha Kouznetsove Jørgensen"
date: "2023-05-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Each iteration represents a day. 
There are students, ai_agents and teachers. 
Students can interact with other students, ai_agents and teachers depending on their social_category. 
When students interact, they gain knowledge. 
There can only be one interaction per iteration. (i.e day).


This is a description of the attributes of the agents, which interactions are based on:



#Attention: Represents cognitive abilities of the student. Attention modulates learning. 

#interaction_type: Shows who the student in question interacted with. A peer, an ai_agent or a teacher or none. 

#prior knowledge: Measure of knowledge (about a topic) beforehand. This variable is resampled for each tick, assuming prior knowledge is different for different topics. 


#Knowledge_gain: Defined as amount of extra knowledge a student acquires from an interaction. 


#Social skills: Represents resistance to social norms, conformity, high levels of confidence etc.  
  Social skills determines your social category:
  0-33.33 social skills = 'low': No interaction or interact with ai_agents only based on assumptions of fear of embarassement
  
  33.33-66.66 social skills = 'medium': interactions with ai_agents and peers. Or no interacction and peers.  Based on assumptions that you are not embarrassed to ask your peers, but you have a fear of embarrassesing yourself by talking to your teacher. 
  
  66.66-99.99 social skills = 'high': Possibility of interacting with all three agents with equal probability. Based on assumptions of no fear of embarrassement. 
  

The resulting data frame should contain all these attributes for each student for each iteration/day.




```{r}
pacman::p_load(tidyverse, dyngen, ggplot2, rethinking)
set.seed(7)
```

Set global parameters
```{r}
# Set the number of students, teachers, and AI agents
n_students <- 36
n_teachers <- 1
n_ai_agents <- 36
max_ticks <-  360 #each tick represents one day

```

###Values from survey
```{r}
survey <- read_csv("socult_survey.csv")

mean(survey$preparation) #0.57
sd(survey$preparation) #0.25

mean(survey$`asking questions`) #0.42
sd(survey$`asking questions`) #0.28

mean(survey$`social evaluation`) #0.50, social capacity = 1-0.5
sd(survey$`social evaluation`) #0.29

mean(survey$teacher) #0.94
sd(survey$teacher)#0.06

mean(survey$peers) #0.93
sd(survey$peers) #0.07

```


```{r}
df_long <- survey %>%
  gather(variable, value, -ID)


plt <- ggplot(df_long, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot() +
  labs(title = "Survey responses",
       x = "category",
       y = "Value")

plt + scale_fill_brewer(palette="Blues") + theme_minimal()


```


```{r}
hist(survey$`social evaluation`)
hist(combined_df$social_capacity)

hist(survey$preparation)
hist(combined_df$prior_knowledge)

hist(survey$teacher)
t <- combined_df %>% filter(interaction_type== "teacher")
hist(t$un)
```

Set agent parameters
```{r}
# Define initial values for agent attributes
student<- tibble(
  ID = 1:n_students, 
  Tick = NA,
  interaction_type = NA,
  attention = runif(n_students, 0.0, 1.0),
  social_capacity = rnorm_bounded(n_students, mean=0.5, sd=0.29, min = 0, max = 1),
  prior_knowledge = rnorm_bounded(n_students, mean=0.47, sd=0.25, min = 0, max = 1),
understanding_of_context = rnorm_bounded(n_students, mean=0.93, sd=0.07, min = 0, max = 1),
  information_gain = 0,
  knowledge_gain = NA,
 ) 


teacher <- tibble(
  ID = n_teachers,
  information = 1,
  understanding_of_context = 0.94
)

ai_agent <- tibble(
  ID = 1:n_ai_agents, 
  information = 1,
  understanding_of_context = runif(n_ai_agents, 0, 1)
  )
  
```

```{r}
hist(student$prior_knowledge, xlim =0:1)
```



#### AI_Environment ####
```{r with social skills}

interaction_loop <- function(student, ai_agent, teacher, n_students, max_ticks){
  df <- tibble(
    ID = integer(), 
    Tick = integer(),
    interaction_type = character(),
    social_capacity = numeric(),
    attention = numeric(),
    prior_knowledge = numeric(),
    understanding_of_context = numeric(),
    information_gain = numeric (),
    knowledge_gain = numeric()
    
  ) 
  
  #For each student
    for (i in 1:n_students){
      student$attention[i] <- runif(n_students, 0.0, 1.0)
      student$social_capacity[i] <-  student$social_capacity[i]
      student$prior_knowledge[i] <-rnorm_bounded(n_students, mean=0.5, sd=0.15, min = 0, max = 1)
    
      
          if (student$social_capacity[i] < 0.33) { 
              j <- sample(1:n_ai_agents, 1)  #interact with 'random' ai
              student$interaction_type[i] <- "ai_agent"
              
              student$information_gain[i] <- ai_agent$information[j]*ai_agent$understanding_of_context[j]*student$attention[i]
              student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
                 
                }
              
                
              
        if (between(student$social_capacity[i], 0.33,0.66)){
              
              if (runif(1) <= 0.5) { #two options of interaction
                 
                 k <- sample(1:n_ai_agents, 1)  #interact with 'random' ai
              student$interaction_type[i] <- "ai_agent"
                  
              student$information_gain[i] <- ai_agent$information[k]*ai_agent$understanding_of_context[k]*student$attention[i]
              student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
                  
                  }
              
            
            else {
                 other_student <- sample(setdiff(1:n_students, i), 1)  # Choose a random student to interact with
            student$interaction_type[i] <- "peer"
            
                 student$information_gain[i] <- student$prior_knowledge[other_student]*student$understanding_of_context[other_student]*student$attention[i] 
            student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
        
            }
        }
            
            
          if(student$social_capacity[i] > 0.66){
             event <- sample(1:3, 1)
             
             if(event == 1){ #interact with ai
                h <- sample(1:n_ai_agents, 1) 
              student$interaction_type[i] <- "ai_agent"
                  
                  student$information_gain[i] <- (ai_agent$information[h]*ai_agent$understanding_of_context[h]) * student$attention[i]
              student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
                  }
              
             
              if(event == 2){ #interact with other student
               other_student <- sample(setdiff(1:n_students, i), 1) 
               student$interaction_type[i] <- "peer"
            
                 student$information_gain[i] <- student$prior_knowledge[other_student]*student$understanding_of_context[other_student]*student$attention[i] 
            student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
                  
                  }
            
             
             if(event == 3){ #interact with teacher
               student$interaction_type[i] <- "teacher"
               student$information_gain[i] <- (teacher$information * teacher$understanding_of_context) * student$attention[i]
               student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
               }
            }
          
      
          
      
   df <- df %>% rows_insert(student[i,], conflict = "ignore")
    }
return(df)
  
}
```

```{r}
res <- interaction_loop(student, ai_agent, teacher, n_students, max_ticks)
```

```{r}
df_3 <- list ()
df_3 <- lapply(1:max_ticks, function(x) interaction_loop(student, ai_agent, teacher, n_students, max_ticks)) #reach student makes an interaction a day, for 360 days 
##NB: takes quite a while to run

```

```{r}
ABM_ai <- df_3 %>% bind_rows() #combine all nested data frames to one big data frame
```

```{r}
tt <- ABM_ai %>% mutate(Tick = rep(1:360, each = 36))
tt$understanding_of_context[tt$interaction_type == "teacher"] <- 0.94 #something went wrong during the loop

#ABM_ai_df <- tt %>% mutate(social_cat = case_when(
    #social_capacity <=0.33 ~ 'low', 
    #between(social_capacity, 0.33, 0.66)  ~ 'medium',
    #social_capacity >=0.66 ~ 'high'))
```

```{r}
write.csv(ABM_ai_df, "Socult_ABM_df_final.csv")
```

### No AI Environment ####

```{r no ai}

interaction_loop_no_ai <- function(student, teacher, n_students, max_ticks){
  df <- tibble(
    ID = integer(), 
    Tick = integer(),
    interaction_type = character(),
    social_capacity = numeric(),
    attention = numeric(),
    prior_knowledge = numeric(),
    understanding_of_context = numeric(),
    information_gain = numeric (),
    knowledge_gain = numeric()
    
  ) 
  
  #For each student
    for (i in 1:n_students){
      student$attention[i] <- runif(n_students, 0.0, 1.0)
      student$social_capacity[i] <-  student$social_capacity[i]
      student$prior_knowledge[i] <-rnorm_bounded(n_students, mean=0.5, sd=0.15, min = 0, max = 1)
            
          if (student$social_capacity[i] < 0.33) { 
              j <- sample(1:n_ai_agents, 1)  #interact with 'random' ai
              student$interaction_type[i] <- "no_interaction"
              
              student$information_gain[i] <- 0
              student$knowledge_gain[i] <- 0
                 
                }
              
                
              
        if (between(student$social_capacity[i], 0.33,0.66)){
              
              if (runif(1) <= 0.5) { #two options of interaction
                 
                 k <- sample(1:n_ai_agents, 1)  #interact with 'random' ai
              student$interaction_type[i] <- "no_interaction"
                  
              student$information_gain[i] <- 0
              student$knowledge_gain[i] <- 0
                  
                  }
              
            
            else {
                 other_student <- sample(setdiff(1:n_students, i), 1)  # Choose a random student to interact with
            student$interaction_type[i] <- "peer"
            
                 student$information_gain[i] <- student$prior_knowledge[other_student]*student$understanding_of_context[other_student]*student$attention[i] 
            student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
        
            }
        }
            
            
          if(student$social_capacity[i] > 0.66){
             event <- sample(1:3, 1)
             
             if(event == 1){ #interact with ai
                h <- sample(1:n_ai_agents, 1) 
              student$interaction_type[i] <- "no_interaction"
                  
                  student$information_gain[i] <- 0
              student$knowledge_gain[i] <- 0
                  }
              
             
              if(event == 2){ #interact with other student
               other_student <- sample(setdiff(1:n_students, i), 1) 
               student$interaction_type[i] <- "peer"
            
                 student$information_gain[i] <- student$prior_knowledge[other_student]*student$understanding_of_context[other_student]*student$attention[i] 
            student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
                  
                  }
            
             
             if(event == 3){ #interact with teacher
               student$interaction_type[i] <- "teacher"
               student$information_gain[i] <- teacher$information*teacher$understanding_of_context*student$attention[i]
               student$knowledge_gain[i] <- student$information_gain[i]/(1+student$prior_knowledge[i])
               }
            }
          
      
          
      
   df <- df %>% rows_insert(student[i,], conflict = "ignore")
    }
return(df)
  
}
```

```{r}
res_no_ai <- interaction_loop_no_ai(student, teacher, n_students, max_ticks)
```

```{r}
df_no_ai <- list ()
df_3_no_ai <- lapply(1:max_ticks, function(x) interaction_loop_no_ai(student, teacher, n_students, max_ticks))
```

```{r}
no_ai <- df_3_no_ai %>% bind_rows() #combine all nested data frames to one big data frame
```

```{r}
ABM_no_ai <- no_ai %>% mutate(Tick = rep(1:360, each = 36))
ABM_no_ai$understanding_of_context[ABM_no_ai$interaction_type == "teacher"] <- 0.94 #something went wrong during the loop

ABM_no_ai_df <- ABM_no_ai %>% mutate(social_cat = case_when(
    social_capacity <=0.33 ~ 'low', 
    between(social_capacity, 0.33, 0.66)  ~ 'medium',
    social_capacity >=0.66 ~ 'high'))
```

```{r}
write.csv(ABM_no_ai_df, "Socult_ABM_df_final_no_ai.csv")
```
rbind(final)
```{r}
combined_df <- rbind(ABM_ai_df, ABM_no_ai_df)
```







